E-jection fraction - Tracking how your website pumps out E-Mails

### 2016-05-15 Results/disclosure.tex
chap5 prelim edits done added table for dev responses

Out of the \domains\ vulnerable domains found, only 108 websites had the mailboxes specified above set-up to receive e-mails. For the remaining domains, we used the \dq{\texttt{whois}}~\cite{whois} data to get the contact details of the owner, and then e-mailed them with the same disclosure data.

>>>>

Out of the \domains\ vulnerable domains found, only 108 websites had the mailboxes specified above set-up to receive e-mails. For the remaining domains, we used the \texttt{whois}~\cite{whois} data to get the contact details of the owner, and then e-mailed them with the same disclosure data. The number of emails we sent out and the number of developer responses we received is shown in Table~\ref{tab:devresp}.

\begin{table}
\centering
\begin{tabular}{|c|c|c|}
	\hline
	\multicolumn{1}{|p{2cm}}{\centering \textbf{E-Mailed websites}} &
	\multicolumn{1}{|p{2cm}|}{\centering \textbf{Developer Responses}} &
	\multicolumn{1}{p{2cm}|}{\centering \textbf{Confirmed discoveries}}\\
	\hline
	293 & 13 & 9 \\
	\hline
\end{tabular}
	\caption[\titlecap{Data gathered by our pipeline}]{Responsible disclosure of the discovered vulnerabilities to developers and the number of received responses.}
	\label{tab:devresp}
\end{table}
